Maps

### 2020-04-27 ms_8.Rmd
Commit backup app code

```{r workingApp}
# START THE APP

@@

@@

@@

@@

@@

>>>>

```{r workingApp}
#
# This is a Shiny web application. You can run the application by clicking
# the 'Run App' button above.
#
# Find out more about building applications with Shiny here:
#
#    http://shiny.rstudio.com/
#

# LOAD THE REQUIRED PACKAGES

library(shiny)
library(haven)
library(tidyverse)
library(gt)
library(devtools)
library(tibble)
library(foreign)
library(scales)
library(shinythemes)
library(plotly)
library(leaflet)
library(broom)
library(patchwork)
library(magick)
library(giphyr)
library(gridExtra)

# READ IN THE DATA

# Read in the model for gt and plot

maleedu_model <- readRDS("maleedu_model.rds")

# Read in the shapefiles

shapefiles <- readRDS(file = "shapefiles.rds")

# Read in the dataset made specifically for mapping

x <- readRDS("mwData.rds")

# Now subset by year

# I tried saving these as Rds files as well, but I kept getting a weird error
# Might be a bug, according to SO
Census_1870 <- x %>% filter(YEAR == "1870") %>%
    select_if(~ !all(is.na(.))) %>%
    select(-STATEA:-GISJOIN & -COUNTY)

# If I put "Census_1870" = "1870", would only the year show up in dropdown menu?
data_sets <- c("1870" = "Census_1870", "1880" = "Census_1880", "1890" = "Census_1890", "1900" = "Census_1900", "1910" = "Census_1910", "1920" = "Census_1920",  "1930" ="Census_1930",  "1940" ="Census_1940",  "1950" ="Census_1950",  "1960" ="Census_1960")

# Read in the dataset for maps and models

# START THE APP

@@

               tabPanel("Introduction",
                        titlePanel("A Brief Overview of Midwest Agriculture"),

                        # Create a spot for the plot
                        # Why is the text on top of the image?? :(
                        mainPanel(
                            tabsetPanel(id = "tabsMain",
                                        tabPanel("Farms & Acreage",

                                                 # Create a fluid row in order to comment next to the gifs
                                                 # column specifications might need to be changed

                                                 fluidRow(column(width = 3, textOutput("acre_com")),
                                                          column(width = 9, align = "center",
                                                                 imageOutput("acre_gif")))

                                        ),
                                        tabPanel("Urbanization",
                                                 # Generate a row with a sidebar
                                                 fluidRow(column(width = 3, textOutput("pop_com")),
                                                              column(width = 9, align = "center",
                                                                     imageOutput("pop_gif")))
                                                 ),
                                        tabPanel("Mechanization",
                                                fluidRow(column(width = 3, textOutput("plot2_com")),
                                                              column(width = 9, align = "center",
                                                                     imageOutput("plot2")))
                            )))),

               tabPanel("Models",

                        # Give the page a title
                        titlePanel("Agriculture and Education, by County"),

                        # Create a spot for the plot
                        mainPanel("",
                                  tabsetPanel(id = "tabsMain",

                                              tabPanel("Implements and Education",
                                                       # Generate a row with a sidebar
                                                       sidebarLayout(

                                                           # Define the sidebar with one input
                                                           # comprehensive options:
                                                           # c("1870" = "1870", "1880" = "1880", "1890" = "1890", "1900" = "1900","1910" = "1910", "1920" = "1920", "1930" = "1930", "1940" = "1940", "1950" = "1950", "1960" = "1960")
                                                           sidebarPanel(
                                                               selectInput("impYear", "Year:", 
                                                                           choices=c("1870" = "1870", "1890" = "1890", "1910" = "1910", "1920" = "1920", "1930" = "1930", "1940" = "1940"), 
                                                                           multiple = TRUE)),
                                                           helpText("*Enter help text*")
                                                       ),

@@

                                                       plotOutput("impedu_plot"),
                                                       p("say some stuff")
                                              ),

                                              tabPanel("Cattle and Education",
                                                       # Generate a row with a sidebar
                                                       sidebarLayout(

                                                           # Define the sidebar with one input
                                                           # comprehensive options:
                                                           # c("1870" = "1870", "1880" = "1880", "1890" = "1890", "1900" = "1900","1910" = "1910", "1920" = "1920", "1930" = "1930", "1940" = "1940", "1950" = "1950", "1960" = "1960")
                                                           sidebarPanel(
                                                               selectInput("cowYear", "Year:", 
                                                                           choices=c("1870" = "1870", "1890" = "1890", "1910" = "1910"), 
                                                                           multiple = TRUE)),
                                                           helpText("*Enter help text*")
                                                       ),

                                                       plotOutput("agPlot"),
                                                       p("Number of cows might be seen as a stand in for farm size. Is it?")
                                              ),

                                              tabPanel("Gender and Education",

                                                       #mainPanel("",
                                                                 #gt_output("maleedu_gt"))

                                                       fluidRow(column(width = 6, plotOutput("maleedu_plot")),
                                                                column(width = 6, #align = "center",
                                                                       gt_output("maleedu_gt")))

                                              )
                                  )
                        )),

@@

                        # Give the page a title
                        titlePanel("About this project"),
                        p("My name is Julia Englebert. I am a senior at Harvard College studying Near Eastern Languages and Civilizations with a secondary field in Ethnicity, Migration, and Rights. Some of my academic interests include the history and future of Midwestern agriculture, and the role of data science in shaping social policy."),
                        br(),
                        p("This project uses historical census and American Community Survey (ACS) data to explore correlations between agriculture and education in the Midwestern United States. By joining the two datasets, the former containing agricultural data and the later containing demographic data, I was able to look at the impact of farming, land value, crop value, and more on education in Midwestern communities over the course of a century. I chose this particular time range in part because of the data that was available to me, and in part due to the economic, industrial, and education policy changes that ocurred from 1870 to 1960. My data is sourced from the IPUMS National Historical Geographic Information System (NHGIS) at nhgis.org. IPUMS provides census data from around the world, but my project focuses specifically on the United States from 1870 to 1960. All datasets and gis files used for this project can be downloaded from the NHGIS Data Finder:"),
                        p(a(href="https://data2.nhgis.org/main", "NHGIS Data Finder")),
                        br(),
                        p("To see more of my work, please visit my Github account:"),
                        p(a(href="https://github.com/julia-englebert", "Julia Englebert")),
                        br(),
                        titlePanel("Citations"),
                        p("Steven Manson, Jonathan Schroeder, David Van Riper, and Steven Ruggles. IPUMS National Historical Geographic Information System: Version 14.0 [Database]. Minneapolis, MN: IPUMS. 2019. http://doi.org/10.18128/D050.V14.0"),
                        p("The College of William and Mary and the Minnesota Population Center. School Attendance Boundary Information System (SABINS): Version 1.0. Minneapolis, MN: University of Minnesota 2011.")
               ),

               tabPanel("Codebook",
                        titlePanel("How were variables measured for this project?"),
                        p("Put some info here. An interactive gt table would be nice if you have time."))
    )
)

@@

    output$acre_com <- renderText({

        "This is the commentary about farm acreage"
    })

    output$acre_gif <- renderImage({
        list(src = "acre_gif.gif")

    }, deleteFile = FALSE)

    output$pop_com <- renderText({

        "This is the commentary about population"
    })

    output$pop_gif <- renderImage({
        list(src = "pop_gif.gif")

    }, deleteFile = FALSE)

    output$plot2_com <- renderText({

        "This is the commentary about mechanization"
    })

    output$plot2 <- renderImage({
        list(src = "plot2.gif")

    }, deleteFile = FALSE)

    # Implements plot

    output$impedu_plot <- renderPlot({

        allData %>%
            filter(YEAR %in% input$impYear) %>%
            mutate(YEAR = as.factor(YEAR)) %>%
            mutate(YEAR = fct_explicit_na(YEAR, na_level = NA)) %>%
            group_by(YEAR) %>%
            select(YEAR, avg_value_implements, pct_enrolled) %>%
            na.omit() %>%
            ggplot(aes(x = avg_value_implements, y = pct_enrolled, color = YEAR)) + 
            geom_point(alpha = 0.1) +
            geom_smooth(method = "lm", se = FALSE) +
            scale_fill_viridis_d(aesthetics = "color") +
            ylim(0, 45) + 
            labs(title = "Relationship Between Farm Implements and Education, by County",
                 subtitle = "Midwestern United States", 
                 x = "Average Value of Implements", 
                 y = "Percent Population Enrolled in School") +
            scale_x_log10(labels = comma) +
            theme_classic()
    })

@@

        # Render a plot
        allData %>%
            filter(YEAR %in% input$cowYear) %>%
            mutate(YEAR = as.factor(YEAR)) %>%
            mutate(YEAR = fct_explicit_na(YEAR, na_level = NA)) %>%
            group_by(YEAR) %>%
            select(YEAR, cows_per_farm, pct_enrolled) %>%
            na.omit() %>%
            ggplot(aes(x = cows_per_farm, y = pct_enrolled, color = YEAR)) +
            geom_point(alpha = 0.1) +
            geom_smooth(method = "lm", se = FALSE) +
            scale_color_viridis_d() +
            ylim(0, 45) +
            scale_x_log10(labels = comma) +
            labs(title = "Cows and Education",
                 subtitle = "Relationship between the number of cows per farm\nand school enrollment, by county",
                 x = "Average Cows per Farm",
                 y = "Percent of Population Enrolled in School") +
            theme_classic()
    })

    # maleedu plot and gt

    output$maleedu_plot <- renderPlot({
        maleedu_model %>%
            ungroup() %>%
            select(YEAR, pct_male_coef, pct_male_upper, pct_male_lower) %>%
            mutate(YEAR = as.factor(YEAR)) %>%
            group_by(YEAR) %>%
            ggplot(aes(x = YEAR, y = pct_male_coef)) + 
            geom_errorbar(ymin = maleedu_model$pct_male_lower, ymax = maleedu_model$pct_male_upper, color = "#453781FF") + 
            geom_point(color = "#440154FF") +
            theme_classic() +
            ylim(-1.5, 0.5) + 
            labs(x = "Year",
                 y = "Coefficient",
                 title = "Percent Male Coefficients Over Time",
                 subtitle = "Measuring the effect of being male\non school enrollment")
    })

    output$maleedu_gt <- render_gt({
        maleedu_model%>%
            ungroup() %>%

    # Map output
